Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-02 p2/axiom-proof.tex
More proofs

In this section we offer proofs for the \namecrefs{ax_separate_commute} listed in
\cref{rules_lemma}.
For the purposes of the proofs we extend the notion of filesystems 
to the full set of functions mapping $\setn$ to $\setv$, even if they
do not have the tree property.
In this case we continue to say that the filsystem is broken,
but we also describe the filesystem values at certain nodes.
Also, in order to pinpoint the region that violates the tree property,
we say that the filesystem is \emph{broken at $n$} if 
$n$ is not a dictionary, but has at least one non-empty child.

Accordingly, we also extend filsystem commands from partial to full functions,
and assume that they return a filesystem we can describe in all cases.
We note that once a filesystem is broken, it stays broken, even if
after a subsequent command it no longer violates the tree property.

It follows from the definition of the tree property that
whether a filesystem is \emph{broken at a node $n$} is determined only
by the values at $n$, $\parentf{n}$, and the children of $n$.
In other words,

@@

Therefore $\czwmv\aFS$ must be broken at $\parentf{m}$.
By definition this means that its value at $\parentf{m}$ cannot be a directory.
Also, reasoning similar to the above shows that it is only possible if $\cxynv$ changes
the environment of $\parentf{m}$, which, since $n\indep m$, is only possible
if $n$ and $m$ are siblings.

@@

>>>>

TODO From filesystem definition

In this section we offer proofs for the \namecrefs{ax_separate_commute} listed in
\cref{rules_lemma}.
For the purposes of the proofs we extend the notion of filesystems 
to the full set of functions mapping $\setn$ to $\setv$, even if they
do not have the tree property.
In such cases we continue to say that the filsystem is broken,
but we also continue to describe the filesystem values at nodes in $\setn$.
Also, in order to pinpoint the region that violates the tree property,
we say that the filesystem is \emph{broken at $n$} if 
$n$ is not a dictionary, but has at least one non-empty child.

Accordingly, where needed, we also implicitly extend filesystem commands
so that they would return a filesystem even if it violates the tree property.
They continue to be undefined in cases where their input types are incompatible
with the input filesystem.
We note that once a filesystem is broken, it stays broken, even if
after a subsequent command it would no longer violate the tree property.

It follows from the definition of the tree property that
whether a filesystem is \emph{broken at a node $n$} is determined only
by the values at $n$ and the children of $n$.
In other words,

@@

Therefore $\czwmv\aFS$ must be broken at $\parentf{m}$.
By definition this means that its value at $\parentf{m}$ cannot be a directory.
Also, reasoning similar to the above shows that this is only possible if $\cxynv$ changes
the environment of $\parentf{m}$, which, since $n\indep m$, is only possible
if $n$ and $m$ are siblings.

@@

\begin{proof}
It is easy to see that over any $\setn$ one can construct a filesystem that neither command breaks.
Since $n\indep m$, it is always possible to set all descendants of both $n$ and $m$ empty,
and have a directory at all ancestors of both $n$ and $m$. In such positions any values are permissible,
so neither command will break the filesystem.
\end{proof}

\cref{ax_same_breaks}

\begin{proof}
This is trivial, as either $\cxynv$ breaks the filesystem, or, if it does not, then
we know $[\cxynv\aFS(n)]=[y]\neq [z]$, and therefore $\czwnv$ will break the filesystem.
\end{proof}

\cref{ax_same_emptyseq}

\begin{proof}
From the conditions we see that for every $\FS$,
$\FS$ and $(\cxynv\cc\czwnv)\aFS$ have the same values at every node,
while the latter can still be broken if $\cxynv\aFS$ is broken.
This is equivalent to saying that where the $\cxynv\cc\czwnv$ function is defined,
it is the identity function, that is, it is extended by $\emptyseq$.
\end{proof}

\cref{ax_same_singlec}

\begin{proof}
It is easy to see that where both $\cxynv\cc \czwnv$ and $\cxwnv$ are defined
(they do not break the filesystem), they are equivalent.
What remains to show is that they break the same set of filesystems.
If $(\cxynv\cc \czwnv)\aFS$ is not broken, then we know that neither of
$\FS$, $\fsreplacement{\FS}{n}{y}$ or $\fsreplacement{\FS}{n}{w}$ is broken,
and therefore $\cxwnv$ does not break $\FS$.
Conversely, if $\cxwnv$ does not break $\FS$, then 
we know that $\FS$ and $\fsreplacement{\FS}{n}{w}$ are not broken.
Also, as
either $[x]\neq[\empt]$ or $[w]\neq[\empt]$,
there must be a directory at $\FS(\parentf{n})$,
and so $\fsreplacement{\FS}{n}{y}$ cannot be broken, either,
as any value is permissible at $n$.
This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.
\end{proof}

\cref{ax_directchild_breaks}

### 2018-07-02 p2/axioms.tex
More proofs

\item\mlabel{ax_directchild_breaks}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\cxy\neq\cdd$ and $\czw\neq\cbb$.

>>>>

\item\mlabel{ax_directchild_breaks}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
$\cxypnv\neq\caaaa{x}{y}{\pn}$ and $\czwnv\neq\cbba{n}$.
